\PaperTitle

### 2024-05-05 Final_Report/paper.tex
Wilner defs for scores

These metrics are applicable to all models and allow for
a direct comparison for each of their performances. Two other metrics: precision and recall, help to provide a more detailed understanding of the model's performance on a class-to-class basis.
\newline \\
The equation for \textbf{Accuracy}: \\
\[
Accuracy= \frac{TP + TN}{TS}
\]
\newline \\
The equation for \textbf{Macro F1}: \\
\[
Macro F 1= \frac{1}{n} \sum_{1}^{n} \frac{2*Precision_i*Recall_i}{Precision_i+Recall_i}
\]
\newline \\
The equation for \textbf{Recall}: \\
\[
Recall= \frac{TP}{TP + FN}
\]
\newline \\
The equation for \textbf{Precision}: \\
\[
Accuracy= \frac{TP}{TP + FP}
\]
\\
Accuracy straightforwardly measures the probability of correctly identifying a packet based on the rate at which packets are correctly classified in the validation or test sets.

Macro F1 is more opaque in terms of being intuitively understood, but it's a harmonic average of each class's metrics of precision and recall, averaged across all classes

Recall is the calculation of how many classifications the model got correct for a given class, out of the total number of packets truly from that class.

Precision is the calculation of how many classifications that were marked as as class truly belong to each class.

>>>>

These metrics are applicable to all models and allow for
a direct comparison for each of their performances. Two other metrics: precision and recall, help to provide a more detailed understanding of the model's performance on a class-to-class basis.
\newline \\
The equation for \textbf{Accuracy}: \\
\[
Accuracy= \frac{TP + TN}{TS}
\]
\newline \\
The equation for \textbf{Macro F1}: \\
\[
Macro F 1= \frac{1}{n} \sum_{1}^{n} \frac{2*Precision_i*Recall_i}{Precision_i+Recall_i}
\]
\newline \\
The equation for \textbf{Recall}: \\
\[
Recall= \frac{TP}{TP + FN}
\]
\newline \\
The equation for \textbf{Precision}: \\
\[
Accuracy= \frac{TP}{TP + FP}
\]
\\
Accuracy is the score that rates the effectiveness of a model at classification overall (ie. how many it predicted correctly out of the total set).

Macro F1 is the harmonic average of the of precision and recall for every class, and then taking the average of these calculated scores across all classes.

Recall is the calculation of how many the model correctly classified within a class (ie. how many truly belong in that class in the entire dataset). 
Precision is the calculation of how many the model correctly classified within a class (ie. can be thought of as class accuracy).
